О множествах точек на плоскости с целочисленными расстояниями

### 2019-06-09 pps-linear-bound/pps-linear-lower-bound.tex
Fix a typo
Add new language issues
know out -> derive

The most significant breakthrough on the planar case was done by Solymosi~\cite{solymosi2003note},
who proved that $cn \leq d(2,n)$ for a sufficiently small constant $c$.
Following the details of Solymosi's proof carefully,
one can know out that the inequality holds at least for $c = 1/24$.
(See~\cite[Exercise 2.6]{garibaldi2005erdos} for some remarks.)
The constant was improved in~\cite{our-mz-rus} to $1/8$ for all $n$ and in~\cite{our-vmmsh-2018}
to $3/8$ for sufficiently big $n$.

@@

If the take $k=1$ in Lemma~\ref{lem:2k-1_segments},
we obtan the following result (which is exactly~\cite[Lemma 3]{our-vmmsh-2018}).
\begin{corollary}
	\label{cor:only_one_distance_1_on_straight_line}
	Let $M \in \mathfrak{M}(2,n)$ for some $n$ and let $m$ be a straight line.
	Then there is at most one pair of points $M_1,M_2\in M \cap m$
	such that $|M_1 M_2| = 1$.
\end{corollary}

@@

@@

	\item
		estimate vs. bound

>>>>

The most significant breakthrough on the planar case was done by Solymosi~\cite{solymosi2003note},
who proved that $cn \leq d(2,n)$ for a sufficiently small constant $c$.
Following the details of Solymosi's proof carefully,
one can derive that the inequality holds at least for $c = 1/24$.
(See~\cite[Exercise 2.6]{garibaldi2005erdos} for some remarks.)
The constant was improved in~\cite{our-mz-rus} to $1/8$ for all $n$ and in~\cite{our-vmmsh-2018}
to $3/8$ for sufficiently big $n$.

@@

If the take $k=1$ in Lemma~\ref{lem:2k-1_segments},
we obtain the following result (which is exactly~\cite[Lemma 3]{our-vmmsh-2018}).
\begin{corollary}
	\label{cor:only_one_distance_1_on_straight_line}
	Let $M \in \mathfrak{M}(2,n)$ for some $n$ and let $m$ be a straight line.
	Then there is at most one pair of points $M_1,M_2\in M \cap m$
	such that $|M_1 M_2| = 1$.
\end{corollary}

@@

	\item
		contradict with or to ?

@@

	\item
		estimate vs. bound vs. estimation
